---
title: "Map Practice"
author: "Paloma Cartwright"
date: "30/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(raster)
library(dplyr)
library(spData)
library(spDataLarge)
library(tmap)    # for static and interactive maps
library(leaflet) # for interactive maps
library(tidyverse) 
```

## Making Maps 

This is more practice making maps that I needed to do. 

### Styling Maps 

Using `palette` to add colors to the map 

```{r}
tm_shape(nz) + tm_polygons("Population", palette = "Blues")
tm_shape(nz) + tm_polygons("Population", palette = "YlOrBr")
```


### Adding a Compass and Scale 

use `tm_compass()` and `tm_scale_bar()` to add a compass and a scale to the map. 

```{r}
map_nz = tm_shape(nz) + tm_polygons()
map_nz + 
  tm_compass(type = "8star", position = c("left", "top")) +
  tm_scale_bar(breaks = c(0, 100, 200), text.size = 1)
```

### Changing more layout things 

`tm_layout()` has a ton of functions that can be used to change the layout of the maps. 
`tm_style()` has a bunch of different styles. Run `tm_stylecatalogue()` to see what they all are. 

### Using urban_agglomerations

```{r}
urb_1970_2030 = urban_agglomerations %>% 
  filter(year %in% c(1970, 1990, 2010, 2030))

tm_shape(world)+
  tm_polygons() +
  tm_shape(urb_1970_2030) + 
  tm_symbols(col = "black", border.col = "white", size = "population_millions")+
  tm_facets(by = "year", nrow = 2, free.coords = FALSE)
```
## Creating an Inset Map 

### Step 1: Creating the Region
```{r}
nz_region = st_bbox(c(xmin = 1340000, xmax = 1450000,
                      ymin = 5130000, ymax = 5210000),
                    crs = st_crs(nz_height)) %>% 
  st_as_sfc()
```


### Step 2: Creating the Base Map 

```{r}
nz_height_map = tm_shape(nz_elev, bbox = nz_region) +
  tm_raster(style = "cont", palette = "YlGn", legend.show = TRUE) +
  tm_shape(nz_height) + tm_symbols(shape = 2, col = "red", size = 1) +
  tm_scale_bar(position = c("left", "bottom"))
```

### Step 3: Creating the Inset Map

```{r}
nz_map = tm_shape(nz) + tm_polygons() +
  tm_shape(nz_height) + tm_symbols(shape = 2, col = "red", size = 0.1) + 
  tm_shape(nz_region) + tm_borders(lwd = 3) 
```

### Step 4: Combining the Parts 

You combine the parts using the `viewport()` function. 

```{r}
library(grid)
nz_height_map
print(nz_map, vp = viewport(x = 0.8, y = 0.27, width = 0.5, height = 0.5)) 

```


## Making an inset map of the US 

### Continental US 

```{r}
us_states_map = tm_shape(us_states, projection = 2163) + tm_polygons() + 
  tm_layout(frame = FALSE)
us_states_map
```

### Hawaii and Alaska 

```{r}
hawaii_map = tm_shape(hawaii) + tm_polygons() + 
  tm_layout(title = "Hawaii", frame = FALSE, bg.color = NA, 
            title.position = c("LEFT", "BOTTOM"))
alaska_map = tm_shape(alaska) + tm_polygons() + 
  tm_layout(title = "Alaska", frame = FALSE, bg.color = NA)
```

### Combining all of them 

```{r}
us_states_map
print(hawaii_map, vp = grid::viewport(0.35, 0.1, width = 0.2, height = 0.1))
print(alaska_map, vp = grid::viewport(0.15, 0.15, width = 0.3, height = 0.3))
```


